### 2019-05-30 ms.tex
Add pr gp to results table.

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{llll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88}\\
& Senegal  & {\bf 12.41} &  12.81\\
& Zambia  & {\bf 154.59} &  154.96\\
& Madagascar  & 39.06 &  {\bf 36.36}\vspace{3mm}\\
Spatial 1 & Indonesia & {\bf 14.77} &  15.08\\
& Senegal  & {\bf 12.39} &  16.56\\
& Zambia  & {\bf 162.74} &  163.74\\
& Madagascar  & 70.72 &  {\bf 61.05}\vspace{3mm}\\
Spatial 2 & Indonesia & {\bf 14.81} &  16.36\\
& Senegal  & {\bf 12.31} &  15.91\\
& Zambia  & {\bf 135.39} &  184.14\\
& Madagascar & 67.73 &  {\bf 44.05}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

>>>>

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for all three cross-validation experiments.}}
\begin{tabular}{lllll}
\hline
{\bf CV scheme} & {\bf Country} &  {\bf Polygons} & {\bf Joint} & {\bf Prevalence Cov} \\
\thickhline 
Random & Indonesia  & 13.95 &  {\bf 13.88} & 14.09  \\
& Senegal  & 12.41 &  12.81 &  {\bf 12.37}\\
& Madagascar  & 39.06 &  36.36 &  {\bf 35.82} \vspace{3mm}\\
Spatial 1 & Indonesia & {\bf 14.77} &  14.97 &   {\bf 14.77}\\
& Senegal  & 13.07 &  15.15 &  {\bf 12.21}  \\
& Madagascar  & 70.72 &  61.05 & {\bf 50.38}\vspace{3mm}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate against out-of-sample observed data for three countries.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}
